Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
cosmit
image curves

Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
for correlation, GTE and partial correlation on the \textcolor{red}{normal-?}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC.

Two reasons might explain such overwhelming difference: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator could be reduced to a linear model after
pre-processing. \textcolor{red}{Those results generalized over the other
datasets see Appendix REF.}

\textcolor{red}{TODO: depth discussion }

@@

\begin{figure}[bth]
\centering
\includegraphics[width=0.6\linewidth]{images/curves}
\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}
         $\tau=0.11$}
\label{fig:curves}
\end{figure}

>>>>

Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
for correlation, GTE and partial correlation on the \textit{normal-2}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC.

Two reasons might explain such overwhelming difference: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator could be reduced to a linear model after
pre-processing. Those results is obviously generalized over the other
datasets see Appendix \textcolor{red}{REF}.

@@

\begin{figure}[bth]
\centering
\includegraphics[width=\linewidth]{images/curves}
\caption{Method precision-recall and roc curves. \textcolor{red}{GENI3?}
         $\tau=0.11$}
\label{fig:curves}
\end{figure}
